
%=== File containing Global Configuration of the report ===%
%                                                          %
% Copyright (C) ISI - All Rights Reserved                  %
% Proprietary                                              %
% Written by Med Hossam <med.hossam@gmail.com>, April 2016 %
%                                                          %
% @author: HEDHILI Med Houssemeddine                       %
% @linkedin: http://tn.linkedin.com/in/medhossam           %
%==========================================================%

%=========== You MUST type your information here ==========%
% global_config.tex file is designed to configure your     %
% cover pages (main, back and black covers)                %
%==========================================================%

%============= Config new columns type ==============%
\newcolumntype{L}{>{\raggedright\arraybackslash}}
\newcolumntype{R}{>{\raggedleft\arraybackslash}}
\newcolumntype{C}{>{\centering\arraybackslash}}
%==================================================%

%========= Config the cover section ==========%

\title{Distribution et monitoring d'une extraction des données à large échelle}

\author{Haithem FRAD}
%%% if necessary
% Set isBinomal to true and type second author name
%\setboolean{isBinomal}{true}
%\secondAuthor{Prénom NOM}

\diplomaName{Diplôme National d'Ingénieur en Informatique}
\speciality{Ingénierie des Systèmes Intelligents}
%\speciality{Génie des Télécommunications et Réseaux}
%\speciality{Génie Informatique des Systèmes Industriels}

%% Encadrant professionnel
\proFramerName{M. Houssem Eddine SAFAR}
\proFramerSpeciality{}

%% Encadrant académique
\academicFramerName{Mme. Raja TLILI }
\academicFramerSpeciality{}

%% Entreprise d'accueil
\companyName{DATAVORA}

%% Année universitaire
\collegeYear{2019 - 2020}

%%%%%% Signatures section %%%%%%

% You can simply remove theses sentences by typing an empty string
% \proSignSentence{}

\proSignSentence{J’autorise l’étudiant à faire le dépôt de son rapport de stage en vue d’une soutenance.}

\academicSignSentence{}

%%% AR
\arabicAbstract{يلخص هذا التقرير العمل الذي تم تنفيذه في إطار مشروع نهاية الدراسة للحصول على دبلوم الهندسة الوطنية في هندسة النظم الذكية داخل شركة \textLR{DATAVORA}.
يتكون العمل من تحقيق نظام بوت عام وموزع لاستخراج البيانات من مواقع التجارة الإلكترونية التي يطلبها العميل. وبالتالي ، لتحقيق هذا الهدف ، لجأنا إلى التقنيات المناسبة لتلبية احتياجاتنا.
عن طريق اختيار \textLR{Python} وأطر عمل \textLR{Django} و \textLR{Scrapy} وأيضًا التفاعل كلغات برمجة وقاعدة بيانات \textLR{ElasticSearch NoSQL}.
يتم تنفيذ التطبيق باستخدام أداة \textLR{PyCharm} باستخدام بنية \textLR{MVT}.

} 

\arabicAbstractKeywords{\textLR{Python}, \textLR{Scrapy}, \textLR{Django}, \textLR{React}, \textLR{ElasticSearch}, \textLR{MVT}, \textLR{PFE}}

%% To use latin characters inside the arabic text
% just put them inside the command \textLR{}
%%%%

%%% FR
\frenchAbstract{Le présent rapport synthétise le travail effectué dans le cadre du projet de fin d'études pour l'obtention du diplôme national d'ingénieur en Ingénierie des Systèmes Intelligents au sein de l’entreprise DATAVORA.
Le travail consiste à la réalisation d’un système de bot générique et distribué pour extraire les données des sites e-commerce demandés par le client. Ainsi, pour mettre en œuvre cet objectif, il y a eu recours aux technologies adéquates pour satisfaire nos besoins.
En optant python et ses Framework Django et Scrapy et aussi React comme langages de programmations et ElasticSearch  base de données NoSQL.
L’implémentation de l’application est effectuée à l’aide de l’outil PyCharm en utilisant l’architecture MVT. }
\frenchAbstractKeywords{Python, Scrapy, Django, React, ElasticSearch, MVT, PFE}

%%% EN
\englishAbstract{This report summarizes the work carried out within the framework of the end-of-studies project for obtaining the national engineering diploma in Intelligent Systems Engineering within the company DATAVORA.
The work consists of the realization of a generic and distributed bot system to extract data from the e-commerce sites requested by the customer. Thus, to implement this objective, we have resorted to the appropriate technologies to meet our needs.
By opting for python and these Django and Scrapy frameworks and also React as programming languages and ElasticSearch for NoSQL database.
The implementation of the application is done using the PyCharm tool using the MVT architecture.}

\englishAbstractKeywords{Python, Scrapy, Django, React, ElasticSearch, MVT, PFE}

%% if you want to get rid of the company address just set the boolean variable to false
% PS : it's optional
\setboolean{wantToTypeCompanyAddress}{true}

\companyEmail{contact@datavora.com}
\companyTel{(+216) 36 36 36 41}
\companyFax{}
\companyAddressAR{45 تونس  شارع اليابان}
\companyAddressFR{45 Avenue du Japon Tunis 1073 - Tunisie}